### 2011-07-27 doc/theses/svirec/kap3.tex
added some new examples

\begin{example}\label{fdrepairExample}
Consider the XML tree $XT$ from Example \ref{example1ref} conforming the DTD $D$ defined below, which is representing a collection of books and the following functional dependency:\\ $\{bib.book, bib.book.written\_by.author.@ano\} \rightarrow bib.book.written\_by.author$ ($@$ denotes the attribute of an element).
\begin{verbatim}
<!ELEMENT bib (book+)>
<!ELEMENT book (written_by, title)>
<!ELEMENT written_by (author+)>
<!ELEMENT author (name)>
<!ATTLIST author ano CDATA>
<!ELEMENT name PCDATA>
<!ELEMENT title PCDATA>
\end{verbatim}
The functional dependency defined above requires that for each book there is only one element author having a given $@ano$ value. Therefore $XT$ does not satisfy the given functional dependency, because two author elements of the same book have the same value of attribute $@ano$. To resolve this data inconsistency, we can use two different repair strategies: 1) changing one of the value of attribute $@ano$; 2) marking one of the elements author as unreliable. Since the first strategy changes only attribute $@ano$, it is preferred to the second strategy, which changes a larger portion of document, since it marks a whole author element as unreliable.
\qed
\end{example}

>>>>

\begin{example}\label{fdrepairExample}
Consider the XML tree $XT$ conforming the DTD $D$ from Example \ref{pathExample}, which is representing a collection of books and the following functional dependency:\\ $\{bib.book, bib.book.written\_by.author.@ano\} \rightarrow bib.book.written\_by.author$ ($@$ denotes the attribute of an element).

The functional dependency defined above requires that for each book there is only one element author having a given $@ano$ value. Therefore $XT$ does not satisfy the given functional dependency, because two author elements of the same book have the same value of attribute $@ano$. To resolve this data inconsistency, we can use two different repair strategies: 1) changing one of the value of attribute $@ano$; 2) marking one of the elements author as unreliable. Since the first strategy changes only attribute $@ano$, it is preferred to the second strategy, which changes a larger portion of document, since it marks a whole author element as unreliable.
\qed
\end{example}
